Cluster Difference Imaging Photometric Survey (CDIPS) II: A Jupiter-Sized Planet in IC~2602

### 2020-05-08 paper/ms.tex
update per phase-fold

\subsection{TESS Photometry}

@@

>>>>

\begin{figure}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Phase-folded transit of \pn.} Gray points are
    2-minute PDCSAP flux measurements, detrended with
    a 0.3-day robust Huber spline (see Section~\ref{subsec:tess}).
    Black points are binned to approximately 1 point per 6 minutes.
    One hundred samples from the posterior are shown with orange lines.
    % The bottom panel shows the residuals.
    \label{fig:phasefold}
	}
\end{figure}

\subsection{TESS Photometry}
\label{subsec:tess}

@@

%TODO: describe 0.3-day robust Huber spline
